Twists of supersymmetric gauge theories

### 2019-08-15 paper.tex
Editing a Lemma about {I^1, I^1}
Screwing around with gamma matrices but it's a mess

\begin{definition}
The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
where \chris{correct sign?}
\begin{align*}
I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
I^{(2)} (Q_1,Q_2 ; \lambda^*) & = - \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
\end{align*}
\end{definition}

We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.
\begin{lemma} \label{onshell_interaction_lemma}
The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
\[\{I^{(1)},I^{(1)}\} = - 2\{S_{\mr{BV}} , I^{(2)}\}.\]
\end{lemma}

\begin{proof}
This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ is exactly  \chris{...}
\end{proof}

@@

In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.  Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.  Indeed, we expand
\begin{align*}
 \{I^{(1)}, I^{(2)}\}  &= \left\{\<A^* , \Gamma(Q, \lambda)\>, \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\>\right\}\\
 &= \left\< A^*\;,\; \Gamma\left(Q, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\> + \\
 &\quad + .
\end{align*}
\chris{include the terms from the other $\lambda^*$ on the third line.} We can rewrite
\chris{...}.

>>>>

\begin{definition}
The off-shell supersymmetry action on complexified Yang-Mills theory on $\RR^{n}$, for $n=3,4,6,10$, is defined to be the cochain
\[I^{(1)} + I^{(2)} \in \clie^\bu(\mc A) \otimes \cloc^\bu(\fL),\]
where 
\begin{align*}
I ^{(1)} (Q ; A, \lambda, A^*, \lambda^*) & = \<A^* , \Gamma(Q, \lambda)\> + \<\lambda^*, \sd F_A Q\> \\
I^{(2)} (Q_1,Q_2 ; \lambda^*) & =  \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> .
\end{align*}
\end{definition}

We can rephrase Lemma \ref{onshell_action_lemma} in terms of these local functionals.
\begin{lemma} \label{onshell_interaction_lemma}
The functionals $I^{(1)}$ and $I^{(2)}$ above satisfy the equation
\[\{I^{(1)},I^{(1)}\} = -2\{S_{\mr{BV}} , I^{(2)}\}.\]
\end{lemma}

\begin{proof}
This is really just an alternative way of writing the statement of Lemma \ref{onshell_action_lemma}.  Indeed, the functional $\{I^{(1)},I^{(1)}\}$ can be computed as 
\begin{align*}
\{I^{(1)},I^{(1)}\} &= \{\<A^* , \delta_Q A\> + \<\lambda^*, \delta_Q \lambda\>, \<A^* , \delta_Q A\> + \<\lambda^*, \delta_Q \lambda\> \} \\
&= 2(\langle A^*, [\delta_{Q}, \delta_{Q}] A \rangle + \langle \lambda^*, [\delta_{Q}, \delta_{Q}] \lambda \rangle) \\
 &= 2(\langle A^*, \delta_{[Q,Q]} A \rangle + \langle \lambda^*, \delta_{[Q,Q]} \lambda \rangle  - \rho(\Gamma(Q,Q)) \sd \dd \lambda - \frac 12(Q, \sd \dd \lambda)Q - \frac 12(Q, \sd \dd \lambda)Q) \\
 &= 2\langle A^*, \delta_{[Q,Q]} A \rangle + 2\langle \lambda^*, \delta_{[Q,Q]} \lambda \rangle - 2\{S_{\mr{BV}} , I^{(2)}\} \\
 &=
\end{align*}
Here we applied Lemma \ref{onshell_action_lemma} on the third line, and on the last line we used the 
\chris{What about that $[Q,Q]$ term?  It looks like the interaction $I_{\mr{trans}}$ associated to the translation $[Q,Q]$.}
\end{proof}

@@

In the next term, \ref{MC_2}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last two summands vanish by Lemma \ref{onshell_interaction_lemma}.  Likewise, in term \ref{MC_3}, the first two summands vanish by Lemma \ref{SUSY_rotation_invariance_lemma}, and the last term vanishes by applying the 3-$\psi$ rule, Theorem \ref{3_psi_thm}.  Indeed, we expand
\begin{align*}
 \{I^{(1)}, I^{(2)}\}  &= \left\{\langle A^* , \Gamma(Q_3, \lambda)\rangle, \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\rangle\right\}\\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right)\right\rangle + \\
 &\quad + \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3 + \frac 12 \left( (Q_2, \rho(A^*)Q_3)Q_1 + (Q_1, \rho(A^*)Q_3)Q_2 \right)\right\rangle \\
 &= \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^*\right)\right\rangle +  \left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle + \\
 &\quad + (Q_2, \lambda^*)\langle A^*, \Gamma(Q_3, Q_1)\rangle + (Q_1, \lambda^*)\langle A^*, \Gamma(Q_3, Q_2)\rangle,
\end{align*}
where we used, on the last line, the fact that $(Q, \rho(v)Q') = \langle v, \Gamma(Q, Q')\rangle$.  We can simplify this expression by manipulating the second summand.  Indeed,
\begin{align*}
\left\langle\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2))\rho(A^*)Q_3\right\rangle &= - \left\langle\lambda^* \;,\; \rho(A^*)\rho(\Gamma(Q_1,Q_2))Q_3\right\rangle - \langle A^*, \Gamma(Q_1,Q_2) \rangle (\lambda^*, Q_3) \\
&= - \left\langle A^*\;,\; \Gamma\left(Q_3, \rho(\Gamma(Q_1,Q_2)) \lambda^* \right)\right\rangle + \langle A^*, \Gamma(Q_1,Q_2) \rangle (Q_3, \lambda^*)
\end{align*}
since \chris{The equality of the first terms looks write when I write it in indices, not sure how to write it coordinate freely.  Also not sure of the sign of the second term.}
\chris{Ok, in earlier notes Pavel claimed that this bracket was the $(123)$-symmetrization of 
\[\langle A^*, \Gamma(Q_1, \rho(\Gamma(Q_2,Q_3))\lambda^*\rangle + (Q_1,\lambda^*)(A^*, \Gamma(Q_2,Q_3)).\]
I don't see that here -- is that true?  Maybe I'm missing a simplification?  If anything I'm seeing only the second term (which the 3-$\psi$ rule doesn't apply to).  Maybe it's the difference of two expressions to which the rule does apply?}.
